On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-03-24 theory.tex
first complete draft abf-theory

\subsection{A Reference Model for Cybersecurity Engineering}\label{sec:vmodel}

\subsection{Abstract System State}\label{sec:systemstate}
The ISO/IEC/IEEE 15288:2015 (System Life Cycle Processes) provides a definition
of system as ``A combination of interacting elements organized to achieve one
or more stated purposes.''\autocite{ISO201515288}.  Therefore, a system can be
considered as a single agent where its interacting elements are the
constituents of the agent itself. For the sake of simplicity we first define a
system as an agent and then extend the definition to a ``combination of
interacting'' agents.  We use the same process of \autocite{Santaca2016abf} but
over slightly different terms. The differences and commonalities with
\autocite{Santaca2016abf} are described in Appendix~\ref{app:abf}.

@@

\subsection{Operational System State}\label{sec:engsystemstate}
When dealing with a specification of a system (i.e. the design if the system
for a specific operation (as a generic operating/operational system),
considering abstract and general concepts such as knowledge, belief, or
information may result to be too abstract for the objectives of the overall engineering
process (e.g. verification and validation).
As an example, we are usually not
interested in information in abstract but to the transfer of that
information, which we call Assertions, made by a subset of agents. 
Therefore, we now define how we consider an agent for the engineering
of CPS.

@@

\begin{definition}{\bf Assertion -- }\label{def:assertion}
	An assertion is an intended transfer of beliefs between
	two agents $a$ and $b$ such that
	\begin{enumerate}[noitemsep]
		\item[$(\interpretation19)$] $\world\models\rassert{a}{b}{P}$ iff
			$\world\models\belief{a}{P}$, 
			$\world\models\neg\belief{a}{\neg P}$, 
			$\world'\models\rcc(\belief{a}{P},\belief{b}{P})$, 
			for all $\world'$ such that $\world\modalrelation\world'$.
	\end{enumerate}
\end{definition}

\begin{definition}{\bf Behavior -- }\label{def:behavior}
	The behavior of an agent is defined as the transformation process (e.g. defined as a
	protocol, or a functional architecture) that determines the
	output-beliefs based on input-beliefs and vice versa (where input-beliefs and
	output-beliefs are beliefs taken as input or output respectively).
	\begin{enumerate}[noitemsep]
		\item[$(\interpretation20)$] $\world\models\bigcup_{\Phi}\believe{s}{\varphi}$ and $\world\models\behave{a}{[\bigcup_{s\in S}\believe{s}{P_{s}}]}$ iff
			$\world\models\belief{a}{P'}$,

@@

\begin{definition}{\bf Fact -- }\label{def:fact}
Facts are a sub-region of Knowledge $\factRegion = \bigcup_\Phi \knows{a}{\varphi}$
	that predicate in a factive way, e.g.
	if $a$ knows that $P$ then $P$, and the region of facts is monotone (no revision).
	\begin{enumerate}[noitemsep]
		\item[$(\interpretation21)$] $\world\models\fact{a}{P}$ iff
			$\world \models \Box P$. 
	\end{enumerate}
\end{definition}

@@

In the quantitative evaluation of a single agent, depicted in Figure~\ref{fig:quantitative},
we argue that only 1 configuration represents the nominal (expected) behavior 
of the agent while the other configurations are either impossible to 
implement or diverge from the intended nominal behavior.

@@

As described beforehand in this section, the collection of Facts shall define
the functional and the physical architecture of an agent, but Assets and
security properties are defined as Facts. Given that understanding
why an Asset is considered as such by the user doesn't necessarily allow
us to better qualify an Asset, we consider the fact of ``being an asset'' as
a Boolean property of an Agent.

\begin{definition}{\bf Asset --}\label{def:asset}
	\fix{mr}{asset def.}
\end{definition}

@@

\subsection{Qualitative Evaluation of Agent Space in $\abf$}\label{sec:agentspace}
While a quantitative analysis reveals how many possible configurations of an
agent (i.e. a system) exist w.r.t. the $\abf$ theory (i.e. $54/125$ in RCC5), a
qualitative analysis of the different configurations describes
the configurations allowed by the $\abf$ theory, and how those configurations can be
categorized.  In Table~\ref{tab:5com} we provide the generic composition table
of RCC5 over 3 regions instantiated over $\abf$, which shows the whole state
space for a single agent. The color coding of the table represents the 
risk function as a risk matrix as we detail afterwards in this Section.

A detailed qualitative categorization of agents over a theory similar to the
$\abf$ theory presented in this article is described in
\autocite{Santaca2016abf} but the differences in the formalization and of the
application requires another in-depth analysis. As depicted in
Figure~\ref{fig:soundness}, the relation between Facts, and Assertions and Behavior
defines the soundness of the design (admissible configurations of Assertions,
Behaviors and, in turn, Beliefs) w.r.t. the specification (what the
specification mandates, such as by the nature of the physical/functional
architectural models). Similarly, the relation between Assertions and Behavior defines the
soundness of the functional architecture.
We categorize agents by first analyzing the relations
between each pair of Regions defining an agent (i.e. $\abf$), and then we
categorize the different agents as tuple of the three Regions.
For the sake of simplicity, soundness is opposed to non-soundness in the following, however,
with the RCC we consider different ``degrees'' of soundness. For example,
in RCC5, if we consider EQ between two Regions as representing soundness, DR over the same Regions
represents non-soundness while PP, PO, PPi represents the different degrees of soundness.

@@

\begin{enumerate}
	\item \Rcc{$\assertionRegion$}{$\behaviorRegion$}, in order to reason
		on the relation between assertions and behavior we first need
		to consider that, by definition, assertions are defined as
		transfer of information between two agents, e.g., $a$ and $b$.
		Therefore, as depicted in Figure~\ref{fig:system-agent}, an
		agent has two main categories of assertions, input and output assertions.
		Given an agent $a$ and a collection of asserted predicates
		$\Phi$, the Input assertions are those received
		by $a$ from an agent $s$ acting as a sender,
		$\rassert{s}{a}{\Phi}$; similarly, output assertions are sent
		from $a$ to a receiver $r$, $\rassert{a}{r}{\Phi}$. We shall consider
		two pairs of regions: 
		\begin{itemize}
			\item \Rcc{$\assertionRegion_{s\rightarrow
				a}$}{$\behaviorRegion$}, where the relation
				between Input-assertions and behavior describes
				the soundness of the execution of the
				functional architecture w.r.t. input
				elicitation. With more details, the ideal
				specification of the functional architecture,
				along with the expected inputs, defines the
				functional behavior of an ideal system.  If all
				the inputs (Assertions) are correctly handled
				in the functional specification (behavior) the
				specification is sound.

			\item \Rcc{$\assertionRegion_{a\rightarrow
				r}$}{$\behaviorRegion$}, where the relation
				between behavior and outputs describes the
				completeness of the behavior defined in the
				specification w.r.t. the input elicitation.
				With more details, if all the outputs
				(assertions) of the functional architecture can
				be produced, the functional architecture is
				complete.
		\end{itemize}
	\item \Rcc{$\behaviorRegion$}{$\factRegion$} (Competence)
	\item \Rcc{$\assertionRegion$}{$\factRegion$} (Honesty)
\end{enumerate}

\Paragraph{Security Requirements} The following security requirement for a CPS specification can be summarized:
\begin{enumerate}
	\item Proper interaction between multiple correctly-behaving agents (in
		contrast with the ``Improper Interaction Between Multiple
		Correctly-Behaving Entities'' defined by the CWE in the
		categorization of ``research concepts'' in
		\autocite{MITRE2020CWEresearch}) is defined as $\eq{\assertionRegion}{\behaviorRegion}$
	\item The equality relation $\eq{\assertionRegion_{s\rightarrow a}}{\behaviorRegion}$
		describes the intended secure behavior as: the beliefs generated by the behavior of the functional architecture
		shall be complete w.r.t. the specified inputs of the agent. Therefore, \emph{the assertions received by an agent or a system
		shall be compliant with the expected inputs of the functional architecture}. For example, the inputs
		of the user of a SW must be sanitized to exclude deviations w.r.t. the expected inputs of the functions
		implemented in the SW. Another example is the type checking between allowed inputs and expected inputs.
\end{enumerate}

\begin{example}
	\begin{itemize}
		\item https://cwe.mitre.org/data/definitions/1000.html highlight diff between CWE ``improper interaction\ldots'' and our ''Proper interatcion\ldots'' and the internal categorization of the classes and base of the subitems of this CWE
	\end{itemize}
\end{example}

\begin{definition}{\bf Security and Insecurity of a System or an Agent --}\label{def:security}
\end{definition}

\begin{definition}{\bf Risk --}
\end{definition}
\begin{definition}{\bf Risk Matrix --}
\end{definition}

@@

Knowledge is the theory itself, an instance is the facts of a design of it. A
testing process tests facts against knowledge as much as we test a cps design
choices against its specification.  Information carries the knowledge of the
negation of the opposite of the information. Therefore an assertion carries the
belief (as a result of the behavior execution) of not the opposite. But, as
Hintikka States in "popper" our previous statement is true if the probability
distribution of the information is representative wrt the causality structure
(i.e. knowledge and facts, see email before). So, based on our theory, the
assertions should have a number between 3 to 5 possible negated meaning, one
per each rcc if reference and not just a negation of the information. Those
negation representative of an insecure configuration on the communication of
the system. In turn, those configurations should categorize all the CWE.  The
fact that weaknesses are generated by mankind but not exploited makes malicious
attacks confined to the hackers (and black-hat hackers). Fix: move black-hat
hackers as subregion of mankind with malicious intent. Describe the intent as a
desire of reaching a breach of a cybersecurity property over an asset (agent of
the system), instead of searching for a specific attack. The tool would then
translate the system from opnet to abf formula. The abf tool generates all the
sat state of the system fix: add state to all def before this text. And we
shall define the causality relation between the different states generated by
the abf tool as chosen nondeterministically from the possible sat states by a
model checker such as nuxmv.

>>>>

\subsection{A Reference Model for Cybersecurity Engineering}\label{sec:vmodel}
In order to describe the $\abf$-theory we briefly introduce the 
engineering concepts (detailed and extended in Section~\ref{sec:engineering})
underlying the $\abf$-theory; namely, the first three stages of the, so called,
engineering V-Model. Our definition is partial and we only use it for the 
sake of simplicity and to better present the theory.

The development process of a new product (a CPS in our case) 
should follow an engineering model. Our reference engineering process 
(inspired by the waterfall V-Model\autocite{waterfallvmodel}), as depicted in
Figure~\ref{fig:simplifiedvmodel}, is structured as the following ordered list
of abstraction refinement steps.
\begin{enumerate}
	\item The process starts with the definition of a \emph{specification}
		where the general requirements of the CPS are defined (e.g.
		functional, physical, network, and design).  As an example, an
		RFC of a communication or security protocol can be considered
		as the result of this first phase (e.g. see
		RFC-1\autocite{rfc1}.  In this first phase, we consider the
		architectural aspects of a CPS such as the draft physical and
		functional architectures.
	\item The process then continues with the definition of a design where
		the requirements of the previous phase holds; detailing the
		logic of the physical (e.g. the physical-layer encoding of the
		information) and functional architectures (e.g. the protocol
		logic of communication over a number of potential sessions).
	\item Finally, the design is implemented as hardware (HW) for the physical architecture
		and software (SW) for the functional architecture.
\end{enumerate}

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{vmodel.pdf}
	\caption{Cybersecurity Engineering Life-cycle}
	\label{fig:simplifiedvmodel}
\end{figure}

\subsection{Abstract System}\label{sec:systemstate}
The ISO/IEC/IEEE 15288:2015 (System Life Cycle Processes) provides a definition
of system as ``A combination of interacting elements organized to achieve one
or more stated purposes.''\autocite{ISO201515288}.  Therefore, a system can be
considered as a single agent where its interacting elements are the
constituents of the agent itself. For the sake of simplicity we first define a
system as an agent and then extend the definition to a ``combination of
interacting'' agents.  We use the same process of \autocite{Santaca2016abf} but
over slightly different terms. The differences and commonalities with
\autocite{Santaca2016abf} are described in Appendix~\ref{app:abf}.

@@

\subsection{Operational System}\label{sec:engsystemstate}
When dealing with a specification of a system (i.e. the design if the system
for a specific operation (as a generic operating/operational system),
considering abstract and general concepts such as knowledge, belief, or
information may result to be too abstract for the objectives of the overall engineering
process (e.g. verification and validation).
As an example, we are usually not
interested in information in abstract but to the transfer of that
information, which we call Assertions, made by a subset of agents. 
Therefore, we now define how we consider an agent for the engineering
of CPS.

@@

\begin{definition}{\bf Assertion -- }\label{def:assertion}
	An assertion (\fix{mr}{subtype of Information}) of  is an intended transfer of beliefs between
	two agents $a$ and $b$ such that
	\begin{enumerate}[noitemsep]
		\item[$(\interpretation19)$] $\world\models\rassert{a}{b}{P}$ iff
			$\world\models\belief{a}{P}$, 
			$\world\models\neg\belief{a}{\neg P}$, 
			$\world'\models\rcc(\belief{a}{P},\belief{b}{P})$, 
			for all $\world'$ such that $\world\modalrelation\world'$.
	\end{enumerate}
\end{definition}

\begin{definition}{\bf Behavior -- }\label{def:behavior}
	The behavior (\fix{mr}{subtype of Beliefs}) of an agent is defined as the transformation process (e.g. defined as a
	protocol, or a functional architecture) that determines the
	output-beliefs based on input-beliefs and vice versa (where input-beliefs and
	output-beliefs are beliefs taken as input or output respectively).
	\begin{enumerate}[noitemsep]
		\item[$(\interpretation20)$] $\world\models\bigcup_{\Phi}\believe{s}{\varphi}$ and $\world\models\behave{a}{[\bigcup_{s\in S}\believe{s}{P_{s}}]}$ iff
			$\world\models\belief{a}{P'}$,

@@

\begin{definition}{\bf Fact -- }\label{def:fact}
	Facts are a \fix{mr}{sub-region/subtype} of Knowledge $\factRegion = \bigcup_\Phi \knows{a}{\varphi}$
	that predicate in a factive way, e.g.
	if $a$ knows that $P$ then $P$, and the region of facts is monotone (no revision).
	\begin{enumerate}[noitemsep]
		\item[$(\interpretation21)$] $\world\models\fact{a}{P}$ iff
			$\world \models \Box P$. 
	\end{enumerate}
\end{definition}

@@

In the quantitative evaluation of a single agent, depicted in Figure~\ref{fig:quantitative},
we argue that only 1 configuration represents the nominal (expected) behavior 
of the agent while the other configurations are either impossible to 
implement or diverge from the intended nominal behavior. We note 
that, the numbers reported here do not consider the details of the
engineering process and should be considered a limit of an abstract 
representation of the system. In Section~\ref{sec:engineering} we
detail this numeric evaluation to faitfully represent the
number of insecurity configurations.

@@

As described beforehand in this section, the collection of Facts shall define
the functional and the physical architecture of an agent, but Assets and
security properties are defined as Facts, i.e. true. Given that understanding
why an Asset is considered as such by the user doesn't necessarily allow
us to better qualify an Asset, we consider the fact of ``being an asset'' as
a predicate \fix{mr}{(or a true function)} of a component of a system.

\begin{definition}{\bf Asset --}\label{def:asset}
For any agent $a\in Ag$ in a collection of Agents $Ag$, an agent is considered an asset iff 
	\begin{enumerate}[noitemsep]
		\item[$(\interpretation22)$] $\world\models\asset{a}$ iff
			$\world\models \Box\asset{a}$.
	\end{enumerate}
\end{definition}

@@

\subsection{Qualitative Evaluation of Agent Space in $\abf$}\label{sec:agentspace}
While a quantitative analysis reveals how many possible configurations of an
agent (i.e. a system) exist w.r.t. the $\abf$ theory (i.e. $54/125$ in RCC5), a
qualitative analysis of the different configurations describes
the configurations allowed by the $\abf$ theory, and how those configurations can be
categorized.  In Table~\ref{tab:5com} we provide the generic composition table
of RCC5 over 3 regions instantiated over $\abf$, which shows the whole state
space for a single agent. The color coding of the table represents the 
risk function as a risk matrix as we detail afterwards in this section.

A detailed qualitative categorization of agents over a theory similar to the
$\abf$ one, is presented in this article and described in
\autocite{Santaca2016abf}. The differences in the formalization and of the
application requires another in-depth analysis. As depicted in
Figure~\ref{fig:soundness}, the relation between Facts, and Assertions and Behavior
defines the soundness of the design (admissible configurations of Assertions,
Behaviors and, in turn, Beliefs) w.r.t. the specification (what the
specification mandates, such as by the nature of the physical/functional
architectural models). We categorize agents by first analyzing the relations
between each pair of Regions defining an agent (i.e. $\abf$), and then we
categorize the different agents as tuple of the three Regions.
For the sake of simplicity, soundness is opposed to non-soundness in the following, however,
with the RCC we consider different ``degrees'' of soundness. For example,
in RCC5, if we consider EQ between two Regions as representing soundness, DR over the same Regions
represents non-soundness while PP, PO, PPi represents the different degrees of soundness.

@@

\Paragraph{\Rcc{$\assertionRegion$}{$\behaviorRegion$} -- Collaboration}
In order to reason on the relation between assertions and behavior we first
need to consider that, by definition, assertions are defined as transfer of
information between two agents, e.g., $a$ and $b$.  Therefore, as depicted in
Figure~\ref{fig:system-agent}, an agent has two main categories of assertions,
input and output assertions.  Given an agent $a$ and a collection of asserted
predicates $\Phi$, the Input assertions are those received by $a$ from an agent
$s$ acting as a sender, $\rassert{s}{a}{\Phi}$; similarly, output assertions
are sent from $a$ to a receiver $r$, $\rassert{a}{r}{\Phi}$. We shall consider
two pairs of regions\footnote{``I am not asserting, as Lotze did, that a relation between $X$ and $Y$
consists of a quality in $X$ and a quality in $Y$ -- a view which I regard as
quite indefensible. -- I assert that a relation $Z$ between $X$ and $Y$ involves
the existence in $X$ of the quality ``having the relation $Z$ to $Y$'' so that
a difference of relations always involves a difference in quality, and a
change of relations always involves a change of quality.'' --  Ellis J. McTaggart, The Unreality of Time\autocite{Mctaggart1908unreality}}: 
\begin{itemize}
	\item \Rcc{$\assertionRegion_{s\rightarrow a}$}{$\behaviorRegion$},
		where the relation between Input-assertions and behavior
		describes the soundness of the execution of the functional
		architecture w.r.t. input elicitation. With more details, the
		ideal specification of the functional architecture, along with
		the expected inputs, defines the functional behavior of an
		ideal system.  If all the inputs (Assertions) are correctly
		handled in the functional specification (behavior) the
		specification is sound.

	\item \Rcc{$\assertionRegion_{a\rightarrow r}$}{$\behaviorRegion$},
		where the relation between behavior and outputs describes the
		completeness of the behavior defined in the specification
		w.r.t. the input elicitation.  With more details, if all the
		outputs (assertions) of the functional architecture can be
		produced, the functional architecture is complete.
\end{itemize}

\Paragraph{\Rcc{$\assertionRegion$}{$\factRegion$} and \Rcc{$\behaviorRegion$}{$\factRegion$} -- Honesty and Competence}
While Assertions and Beliefs generated by the Behavior determines how a system should work, and the
relation between the two defines the quality (i.e. the completeness w.r.t the specification) of the agent, the relation of
Assertions and Behavior with Facts determines the quality with respect to the
nominal (specified) system.  Given that Facts defines what is true in the
system (e.g. the level of water in a tank may be considered as a Fact, while
the reading of a sensor as a Belief), the relation of Assertions an Facts
determines the degree of quality between the information circulating in a
system (or within an agent) and reality.  Since the transfer of information through Assertions
generates Beliefs, a dishonest agent may circulate false information,
generating false Beliefs.  We note that it is often implied that the intention behind
circulating false information discerns a dishonest and an incompetent agent,
however, we consider honesty related to truth rather than related to what is
true\footnote{``[\ldots] truth exists only in the good man, but the true in the bad
man as well; for it is possible for the bad man to utter something true.''
Sextus Empiricus, Outlines of Pyrrhonism, II-83\autocite{Empiricus1990Pyrrhonism}}.  This implies that the
relation between Beliefs and Facts determines the competence (on the subjected
defined by the Facts) of an agent (i.e. the more competent an agent is, the
more likely a Belief of that agent is true).

\subsubsection{$\abf$ Security Enumeration (SE)} The following security requirement for a CPS specification can be summarized:
\begin{enumerate}
	\item[SE-$1$] Proper interaction between multiple correctly-behaving agents (in
		contrast with the ``Improper Interaction Between Multiple
		Correctly-Behaving Entities'' defined by the CWE--$435$ as one of the top ``view'' of the ``research concepts'' in
		\autocite{MITRE2020CWEresearch}) is defined as $\eq{\assertionRegion_a}{\behaviorRegion_a}$ for an agent $a$
	\begin{enumerate}
		\item[SE-$1.1$] The equality relation $\eq{\assertionRegion_{s\rightarrow a}}{\behaviorRegion_a}$
			describes the intended secure behavior as: the beliefs generated by the behavior of the functional architecture
			shall be complete w.r.t. the specified inputs of the agent. Therefore, \emph{the assertions received by an agent or a system
			shall be compliant with the expected inputs of the functional architecture}. For example, the inputs
			of the user of a SW must be sanitized to exclude deviations w.r.t. the expected inputs of the functions
			implemented in the SW. Another example is the type checking between allowed inputs and expected inputs.
		\item[SE-$1.2$] Similarly, the equality relation $\eq{\assertionRegion_{a\rightarrow r}}{\behaviorRegion_a}$ defines that
			the outputs of an agent $a$ shall be the outputs of the functional architecture.
	\end{enumerate}
	\item[SE-$2$]Sufficient Control Flow Management (in contrast with
		the ``Insufficient Control Flow Management'' defined by MITRE
		in the CWE--$691$ as one of the top ``view'' of the ``research
		concepts'' in\autocite{MITRE2020CWEresearch}) is defined as
		$\eq{\assertionRegion}{\factRegion}$.
	\item[SE-$3$] Correct Calculation (in contrast with the ``Improper
		Calculation'' defined by MITRE in the CWE--$682$ as one of the
		top ``view'' of the ``research concepts''
		in\autocite{MITRE2020CWEresearch}) is defined as
		$\eq{\beliefRegion}{\factRegion}$.
\end{enumerate}

We are now in the position to define what a secure system (with respect to the $\abf$-theory) is
and, based on that definition, what the security risk is and how to quantify it in a risk matrix.
\begin{definition}{\bf Security of a System or an Agent --}\label{def:security}
	A secure system is a system where SE-$1$, SE-$2$, and SE-$3$ holds for each 
	agent composing the system.
\end{definition}
The ISO 31000 consider risk as the ``effect of uncertainty on objectives'' and the refers
both of positive and negative consequences of uncertainty. Accordingly, we consider
risk as follows. 
\begin{definition}{\bf Risk --}
The whole space of potential designs of a specification with respect to the
$\abf$-theory.
\end{definition}
The definition of Risk leads to the risk matrix in Figure~\autoref{fig:quantitative}, defined as follows.
\begin{definition}{\bf Risk Matrix --}
	The risk matrix is a function between the three relations 
	$s=\langle\rcc(\factRegion,\behaviorRegion),\rcc(\factRegion,\assertionRegion),\rcc(\behaviorRegion,\assertionRegion)\rangle$,
	where the maximum risk is defined by the $DR$ relation between the three groups of Regions, and the 
	minimum risk by the $EQ$ relation over the same Regions. In between the two extremes, the granularity
	of possible intermediate configuration is defined by the calculus used (RCC5 in our case).
\end{definition}
We note that often the risk matrix is defined by the relation between likelihood and impact.
We argue that the likelihood is related to the number of possible non secure (i.e. non maximum secure) 
configurations of a system and, similarly, the impact.

@@

Knowledge is the theory itself, an instance is the facts of a design of it. A
testing process tests facts against knowledge as much as we test a cps design
choices against its specification.  Information carries the knowledge of the
negation of the opposite of the information. Therefore an assertion carries the
belief (as a result of the behavior execution) of not the opposite. But, as
Hintikka States in ``popper'' our previous statement is true if the probability
distribution of the information is representative wrt the causality structure
(i.e. knowledge and facts, see email before). So, based on our theory, the
assertions should have a number between 3 to 5 possible negated meaning, one
per each rcc if reference and not just a negation of the information. Those
negation representative of an insecure configuration on the communication of
the system. In turn, those configurations should categorize all the CWE.  The
fact that weaknesses are generated by mankind but not exploited makes malicious
attacks confined to the hackers (and black-hat hackers). Fix: move black-hat
hackers as subregion of mankind with malicious intent. Describe the intent as a
desire of reaching a breach of a cybersecurity property over an asset (agent of
the system), instead of searching for a specific attack. The tool would then
translate the system from opnet to abf formula. The abf tool generates all the
sat state of the system fix: add state to all def before this text. And we
shall define the causality relation between the different states generated by
the abf tool as chosen nondeterministically from the possible sat states by a
model checker such as nuxmv.
